Topological Approach to Finding Blackholes in Directed Networks

### 2019-12-08 blackholes/pavt/article.tex
Start to edit Intro

\begin{document}
\mainmatter              % start of a contribution
%
\title{Topological approach to finding blackholes in directed networks}
%
\titlerunning{Topological black holes mining}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Denis Ivanov\inst{1} \and Alexander Semenov\inst{2}}
%
\authorrunning{Ivanov, Semenov} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Denis Ivanov and Alexander Semenov}
%
\institute{Lomonosov Moscow State University, Moscow, Russian Federation \\
\email{mr.salixnew@gmail.com}
\and
JSC NICEVT, Moscow, Russian Federation\\
\email{semenov@nicevt.ru}
}

@@

\begin{abstract}
In this paper we consider the problem of finding so called Blackhole pattern in directed unweighted graphs.
Firstly, we analyse already existing algorithms and approaches. Secondly, we describe how structure of a graph
affects their efficiency. Then we introduce our approach to graph preprocessing. Finally, we describe topological sort based heuristic
and provide results of experimental comparison between our approach and previously developed algorithm.
\keywords{Directed networks $\cdot$ Subgraph mining}
\end{abstract}

\section{Blackhole Search in Directed Graph}
The task of pattern mining in directed graphs finds its aplications in different areas. In 2010 Li et al.\cite{li2010mining} state
that governments are interested in detecting cases of financial fraud. They formulate the task for finding cases of illegal collaboration, and introduce dual patterns:
blackhole and volcano. Those appear when a group of traders perform operations only between each other in order to manipulate market.
Continuing study of different financial fraud casese, in 2017 Semenov et al. \cite{semenov2017survey} provided a survey of common approaches to anti - money laundering by graph mining.
There are other applications. For example, the online detection of black holes/volcanos can timely 
reflect anomalous events, such as disasters, catastrophic accidents, and therefore help keep public safety \cite{hong2015detecting}.

@@

\begin{figure}[H]
	\includegraphics[width=\linewidth]{rmat.pdf}
	\caption{Algorithm results on RMAT graphs.}
	\label{fig:rmat}
\end{figure}

@@

\begin{figure}[H]
	\includegraphics[width=\linewidth]{ssca2.pdf}
	\caption{Algorithm results on SSCA2 graphs.}
	\label{fig:ssca2}
\end{figure}
\begin{figure}[H]
	\includegraphics[width=\linewidth]{ur.pdf}
	\caption{Algorithm results on Uniform Random graph.}
	\label{fig:ur}
\end{figure}

>>>>

\begin{document}
\mainmatter              % start of a contribution
%
\title{Topological Approach to Finding Blackholes in Directed Networks}
%
\titlerunning{Topological Blackholes Mining}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Denis Ivanov\inst{1} \and Alexander Semenov\inst{2}}
%
\authorrunning{D. Ivanov, A. Semenov} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Denis Ivanov and Alexander Semenov}
%
\institute{Lomonosov Moscow State University, Moscow, Russian Federation \\
\email{mr.salixnew@gmail.com}
\and
JSC NICEVT, Moscow, Russian Federation\\
\email{semenov@nicevt.ru}
}

@@

\begin{abstract}
In this paper we consider the problem of finding so called blackhole pattern in directed unweighted graphs.
Firstly, we analyse already existing algorithms and approaches. Secondly, we describe how structure of a graph
affects their efficiency. Then we introduce our approach to graph preprocessing. Finally, we describe topological sort based heuristic
and provide results of experimental comparison between our approach and the previously developed algorithm.
\keywords{Directed networks $\cdot$ Subgraph mining $\cdot$ Blackhole}
\end{abstract}

\section{Blackhole Search in Directed Graph}
The task of pattern mining in directed graphs finds its aplications in different areas. In 2010 Li et al.\cite{li2010detecting} state
that governments are interested in detecting cases of financial fraud. They formulate the task for finding cases of illegal collaboration, and introduce dual patterns:
blackhole and volcano. Those appear when a group of traders perform operations only between each other in order to manipulate market.
Continuing study of different financial fraud casese, in 2017 Semenov et al. \cite{semenov2017survey} provided a survey of common approaches to anti - money laundering by graph mining.
There are other applications. For example, the online detection of black holes/volcanos can timely 
reflect anomalous events, such as disasters, catastrophic accidents, and therefore help keep public safety \cite{hong2015detecting}.

@@

\begin{figure}[H]
	\includegraphics[width=\linewidth]{rmat.pdf}
	\caption{Algorithm results on RMAT graphs}
	\label{fig:rmat}
\end{figure}

@@

\begin{figure}[H]
	\includegraphics[width=\linewidth]{ssca2.pdf}
	\caption{Algorithm results on SSCA2 graphs}
	\label{fig:ssca2}
\end{figure}
\begin{figure}[H]
	\includegraphics[width=\linewidth]{ur.pdf}
	\caption{Algorithm results on Uniform Random graph}
	\label{fig:ur}
\end{figure}
